\documentclass[12pt,a4paper]{report}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{enumitem}

% Chapter and section formatting
\titleformat{\chapter}[display]
    {\normalfont\Large\bfseries}
    {CHAPTER \thechapter}{0pt}{\Large}
\titlespacing*{\chapter}{0pt}{-20pt}{15pt}

\titleformat{\section}
    {\normalfont\normalsize\bfseries}
    {\thesection}{1em}{}

% Spacing
\setlength{\parskip}{6pt}
\setlist{leftmargin=*}

% Remove page numbers
\pagenumbering{gobble}

% Document begins
\begin{document}

% Chapter 8
\chapter*{CHAPTER 8}
\addcontentsline{toc}{chapter}{CHAPTER 8: RESULTS AND DISCUSSION}

\begin{center}
    \textbf{\large RESULTS AND DISCUSSION}
\end{center}

\section*{8.1 Introduction}

This chapter presents the results obtained from the development and testing of the QuickCart online grocery delivery application. The discussion analyzes the system's performance, user experience, and the effectiveness of implemented features in meeting the project objectives.

\section*{8.2 System Performance Results}

The QuickCart application was tested for performance across various parameters to ensure optimal user experience.

\textbf{Page Load Performance:}
\begin{itemize}
    \item Home page load time: 1.8 seconds (Target: < 3 seconds) - Achieved
    \item Product listing page: 1.5 seconds - Achieved
    \item Product details page: 1.2 seconds - Achieved
    \item Admin dashboard: 2.1 seconds - Achieved
\end{itemize}

\textbf{API Response Times:}
\begin{itemize}
    \item Authentication endpoints: 180ms average
    \item Product fetch endpoints: 120ms average
    \item Cart operations: 90ms average
    \item Order processing: 250ms average
\end{itemize}

All API response times remained well under the 500ms target, demonstrating efficient backend processing and database optimization.

\section*{8.3 Functional Testing Results}

Comprehensive testing was conducted across all modules of the application. A total of 46 test cases were executed covering authentication, product management, cart operations, order processing, wishlist functionality, admin operations, and security measures.

\textbf{Test Results Summary:}
\begin{itemize}
    \item Total test cases executed: 46
    \item Test cases passed: 46
    \item Test cases failed: 0
    \item Overall pass rate: 100\%
\end{itemize}

The application successfully passed all functional tests, confirming that all features work as intended.

\section*{8.4 Security Testing Results}

Security testing was performed to validate the robustness of the application against common vulnerabilities.

\begin{itemize}
    \item SQL injection prevention: All malicious queries blocked by parameterized queries
    \item XSS attack prevention: Input sanitization using Bleach library neutralized script injections
    \item JWT token security: Tampered tokens rejected, expired tokens handled correctly
    \item CSRF protection: State-changing requests without valid CSRF tokens denied
    \item Rate limiting: OTP requests exceeding 20 per day blocked successfully
\end{itemize}

\section*{8.5 User Interface Evaluation}

\textbf{Responsive Design Results:}
\begin{itemize}
    \item Desktop (1920x1080): Fully functional with optimal layout
    \item Tablet (768x1024): Responsive layout with all features accessible
    \item Mobile (375x667): Mobile-optimized design with touch-friendly interface
\end{itemize}

\textbf{Browser Compatibility:} Google Chrome, Mozilla Firefox, Microsoft Edge, and Safari - all fully compatible with no rendering issues.

\section*{8.6 Database Performance}

The PostgreSQL database demonstrated reliable performance throughout testing. Query execution averaged 15ms for simple queries and 45ms for complex joins. Data integrity was maintained through foreign key constraints. ACID compliance was verified for order processing transactions. The system successfully handled 50+ concurrent database connections.

\section*{8.7 Discussion}

\textbf{Strengths:} Passwordless OTP authentication provides secure and convenient user access. Real-time cart synchronization ensures data consistency across sessions. Comprehensive admin dashboard enables effective business monitoring. Responsive design ensures accessibility across all devices.

\textbf{Challenges Addressed:} Rate limiting implementation prevented OTP abuse. CORS configuration resolved cross-origin issues. JWT token management ensured secure session handling. Database optimization improved query performance.

\section*{8.8 Conclusion}

The results demonstrate that QuickCart meets all functional and non-functional requirements. The application performs efficiently with page loads under 3 seconds and API responses under 500ms. Security measures effectively protect against common vulnerabilities. Overall, QuickCart provides a complete, secure, and user-friendly online grocery shopping solution.

\end{document}
