\documentclass[12pt,a4paper]{report}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{hyperref}

% Chapter formatting
\titleformat{\chapter}[display]
    {\normalfont\Large\bfseries}
    {}{0pt}{\Large}
\titlespacing*{\chapter}{0pt}{-20pt}{15pt}

% Spacing
\setlength{\parskip}{6pt}

% Remove page numbers
\pagenumbering{gobble}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue
}

% Document begins
\begin{document}

\begin{center}
    \textbf{\Large REFERENCES}
\end{center}

\vspace{10pt}

\begin{enumerate}

\item R. Sharma and P. Kumar, ``E-Commerce Web Application Development Using React and Node.js,'' \textit{International Journal of Computer Applications}, vol. 175, no. 12, pp. 15-20, 2020.

\item A. Singh and S. Gupta, ``Online Grocery Shopping System: A Review,'' \textit{International Journal of Engineering Research \& Technology}, vol. 9, no. 5, pp. 234-238, 2020.

\item M. Grinberg, \textit{Flask Web Development: Developing Web Applications with Python}, 2nd ed. O'Reilly Media, 2018.

\item A. Banks and E. Porcello, \textit{Learning React: Modern Patterns for Developing React Apps}, 2nd ed. O'Reilly Media, 2020.

\item PostgreSQL Global Development Group, ``PostgreSQL 16 Documentation,'' 2024. [Online]. Available: \url{https://www.postgresql.org/docs/}

\item React Documentation, ``React - A JavaScript library for building user interfaces,'' Meta Platforms, 2024. [Online]. Available: \url{https://react.dev/}

\item Flask Documentation, ``Flask Web Framework,'' Pallets Projects, 2024. [Online]. Available: \url{https://flask.palletsprojects.com/}

\item S. Tilkov and S. Vinoski, ``Node.js: Using JavaScript to Build High-Performance Network Programs,'' \textit{IEEE Internet Computing}, vol. 14, no. 6, pp. 80-83, 2010.

\item OWASP Foundation, ``OWASP Top Ten Web Application Security Risks,'' 2021. [Online]. Available: \url{https://owasp.org/Top10/}

\item J. Duckett, \textit{JavaScript and JQuery: Interactive Front-End Web Development}, Wiley, 2014.

\item K. Chodorow, \textit{MongoDB: The Definitive Guide}, 3rd ed. O'Reilly Media, 2019.

\item BigBasket, ``Online Grocery Shopping Platform,'' [Online]. Available: \url{https://www.bigbasket.com/}

\item Blinkit (formerly Grofers), ``Quick Commerce Grocery Delivery,'' [Online]. Available: \url{https://www.blinkit.com/}

\item Amazon Fresh, ``Online Grocery Delivery Service,'' [Online]. Available: \url{https://www.amazon.in/fresh}

\item Twilio, ``SMS API Documentation,'' 2024. [Online]. Available: \url{https://www.twilio.com/docs/sms}

\item JWT.io, ``JSON Web Tokens Introduction,'' Auth0, 2024. [Online]. Available: \url{https://jwt.io/introduction}

\end{enumerate}

\end{document}
